### 2017-02-13 section/3_redundancy.tex
fix comments from Shan
revise linhai's recent revise

{\color{red}
We calculate the redundancy for an input instruction $I$ based on the
edit-distance between the two sequences of values returned by $I$ in the two
loop instances
and the lengths of the two sequences, denoted by $SeqA$ and $SeqB$. 
The intuition is that the redundancy rate should be 1 if one sequence is the 
sub-sequence of the other; and, the redundancy rate should be 0 if these two
sequences are completely different.
}
The exact formula is the following:
%\[
%\Scale[0.8]{
%min\_dist(SeqA, SeqB) = min(dist(SeqA,SeqB), r\_dist(SeqA, SeqB))
%}
%\]

@@

\Tool suggests a fix strategy for each inefficient loop 
and provides related information for carrying out that strategy.
This process is straightforward following our taxonomy discussion in 
Section \ref{sec:study}, as there are often only one or two natural fix 
strategies for each sub-category of root causes.

>>>>

{\color{red}
We calculate the redundancy for an input instruction $I$ based on the
edit-distance between the two sequences of values returned by $I$ in the two
loop instances
and the lengths of the two sequences, denoted by $SeqA$ and $SeqB$. 
The intuition is that the redundancy rate should be 1 if one sequence is the 
sub-sequence of the other, and be 0 if these two
sequences are completely different.
}
The exact formula is the following:
%\[
%\Scale[0.8]{
%min\_dist(SeqA, SeqB) = min(dist(SeqA,SeqB), r\_dist(SeqA, SeqB))
%}
%\]

@@

{\color{red}
\Tool suggests a fix strategy for each inefficient loop based on the
inefficiency category. Making this suggestion is straightforward for
most categories, and requires a small amount of extra
analysis occasionally. \Tool also
provides related information for carrying out the suggested fix strategy. 
}

\comment{
\Tool suggests a fix strategy for each inefficient loop 
and provides related information for carrying out that strategy.
This process is straightforward following our taxonomy discussion in 
Section \ref{sec:study}, as there are often only one or two natural fix 
strategies for each sub-category of root causes.
}

### 2017-02-13 section/5_exper.tex
revise linhai's recent revise

\textbf{RQ1}.
Can \Tool correctly identify inefficiency categories and suggest fix 
strategies for many real-world loops? (Sec.\ref{sec:coverage})

@@

%\input section/tab_top5
{\color{red}
To answer \textbf{RQ2}, we apply
statistical performance debugging \cite{SongOOPSLA2014} to all our benchmarks
and apply \Tool to the top 5 ranked loops\footnote{Some extracted benchmarks
have fewer than 5 loops. We simply apply \Tool to all loops in these cases.}
to see how accurate \Tool is. 
}
{\color{red}
As shown in Table \ref{tab:benchmarks}, \Tool is accurate, having five real
false positives and 17 benign false positives in total for all the top five loops
of the \allbugs benchmarks.

@@

The five real false positives happen for benchmarks GCC\#8805 and GCC\#12322.
These five loops are identified as
redundant and resultless by \Tool. However, they
are very difficult to fix and hence are not changed in the patches.
Since these five loops are ranked higher than the true positive loops by
statistical debugging, they could cost (waste) \Tool users some effort during 
performance diagnosis. Future work could try to prune these false positives
by estimating the fix difficulty.

\Tool also reports 17 benign false positives.
In these cases, \Tool correctly identified truly inefficient loops.
However, these loops are not the main contributors to the 
performance problems perceived by the users, and hence are not
fixed in patches. 
Different from the five false positives discussed above, these 17 loops are
ranked {\bf lower} than the true positive loops by statistical debugging, as
well as by profillers,
because of their low contributions to the perceived performance problems.
Consequently, they will not cause extra diagnosis effort for \Tool users.
}

>>>>

\textbf{RQ1}.
Can \Tool correctly identify inefficiency categories and fix 
strategies for many real-world loops? (Sec.\ref{sec:coverage})

@@

%\input section/tab_top5
{\color{red}
To answer \textbf{RQ2}, we apply
statistical performance debugging \cite{SongOOPSLA2014} to all benchmarks
and then apply \Tool to the top 5 ranked loops\footnote{Some extracted benchmarks
have fewer than 5 loops. We simply apply \Tool to all loops in these cases.}.
}
{\color{red}
Table \ref{tab:benchmarks} shows that \Tool is accurate, having five real
false positives and 17 benign false positives in total for all the top five loops
of the \allbugs benchmarks.

@@

The five real false positives happen for benchmarks GCC\#8805 and GCC\#12322.
These five loops are identified as
redundant and resultless by \Tool. However, they
are very difficult to fix and hence are not patched.
Since these five loops are ranked higher than the true positive loops by
statistical debugging, they could cost (waste) \Tool users some effort during 
performance diagnosis. Future work could try to prune these false positives
by estimating the fix difficulty.

\Tool also reports 17 benign false positives. These are 
correctly identified inefficient loops.
However, they are not the main contributors to the perceived
performance problems, and hence are not
fixed in patches. 
Different from the five false positives discussed above, these 17 loops are
ranked {\bf lower} than the true positive loops by statistical debugging, as
well as by profillers,
because of their low contributions to the perceived performance problems.
Consequently, they will not cause extra diagnosis effort for \Tool users.
}
